Moral Foundations of U.S. Political News Organizations

### 2024-11-30 manuscript_version/revision/revision_letter.Rmd
rearranging folders and updating the manuscript

thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.

@@

TO DO ADD THE MTMM STUDY FINALLY

@@

TO DO ADD MORE TEXT AND TALK ABOUT THIS STUFF

RESPONSE: [Erin]
- look at original thesis for justification for valence
- note if we add the MTMM, this response may be different, so waiting here. Also this person seems to think that valence ratings are not useful, so add some notes about how they are very predictive, yada yada.
- add information from will's thesis back in there

Critically - also - the MFD was made by just *thinking* about words right? So why is that better than the actual ratings of valence from people?

As noted in text, we z-scored to help with interpretation:

"Valences were z-scored in order to eliminate any ambiguity regarding the direction of the valence. Positive values indicate positive valence, and negative values indicate negative valence."

@@

TO DO MAKE THESE CHANGES

RESPONSE: [Erin]
- move readability stats to an appendix
- undecided here maybe something like ...
Given no page limits for the manuscript, we have opted to include this detail for transparency and openness purposes within the manuscript. Linguistic analysis heavily relies on the pre-processing steps taken on the data, and informing readers on these actions can help contextualize interpretation.

@@

We added an example table of the weighting calculation and rephrased this section completely.

@@

Unfortunately, as with many linguistic analyses that focus on individual words (as with the MFD), context is lost using these approaches. In response to the question about analytic choices, we have added information about a MTMM study, as well as the exact same statistics using the raw percentages.

TO DO - DO THIS

@@

TO DO COMMENT HERE ABOUT THE ORIGINAL SCORING BEING SHIT AS WELL

>>>>

Thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.

@@

The cited manuscript from our original paper was another manuscript the team was working on. We decided to merge those results with this manuscript for stronger evidence about the issues with the MFD. We have rewritten sections to clarify, using the theoretical information proposed by the MFT and other publications, we examined if those results could be found: within several different types of sources and with potential improvements to the MFD. Study 1 now includes our MTMM results.

@@

In our revisions, we have now tested several ideas: 1) if we add more words can we see how the MFD is related to the MFQ (which has good validity evidence)? 2) if that doesn't work, can we augment scores with valence to improve the results? The original MFD was created by simply thinking about words that should relate to the moral foundation areas, and we expand by suggesting new terms through free association and written texts focusing on moral areas. While some frequencies correlate with MFQ results, the relation to the MFQ does not appear to hold with MTMM results.

We examined valence to improve MFD scoring by adding context to the words included. Within one foundation, concepts are both positive and negative. We examined if adding that information would improve the ability to find expected differences. We added citations for justification for valence ratings, as this is very popular technique for sentiment analysis. As noted in text, we z-scored to help with interpretation, as the dataset ranges from 1 to 9, but -1 to 1 is easier to interpret (i.e., greater than zero is positive, less than zero is negative). For comparison, we also provide the results of the traditional scoring, which is to simply calculate the percent of the words within a text.

@@

Given no page limits for the manuscript, we have opted to include this detail for transparency and openness purposes within the manuscript. Linguistic analysis heavily relies on the pre-processing steps taken on the data, and informing readers on these actions can help contextualize interpretation. We have streamlined in method sections when it was repetitive refering back to previous studies.

@@

We added an example table of the weighting calculation and rephrased this section completely for clarity.

@@

Unfortunately, as with many linguistic analyses that focus on individual words (as with the MFD), context is lost using these approaches.

In response to the question about analytic choices, we have added information about a MTMM study (study 1), as well as the exact same statistics using the mean percentages for comparison (study 2-3). The results remain the same.

@@

We added comparisons to the original scoring to demonstrate the results remain the same (study 2 and 3).
